### 2020-10-07 hpp.tex
Finish section on experimental results.

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{figures/construction-set-init.png}
    \includegraphics[width=\linewidth]{figures/construction-set-goal.png}    
  \end{center}
  \caption{Construction set: two robots are requested to assemble magnetic
    spheres on a cylinder from an initial configuration (top) to a goal state
    (bottom).}
  \label{fig:construction-set}
\end{figure}

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|l|l|l|}
    \hline
    & min & max & mean & std dev \\
    \hline
    time (s) & 0.20 & 214.22 & 17.11 & 45.84 \\
    nodes & 10 &  39 & 14.70 & 6.48 \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Experimental results for construction set assembly.}
  \label{tab:construction-set}
\end{table}

In the three previous test cases, the constraint graph was automatically built
following Algorithm~\ref{algo:constraintGraphFactory}. If the number of grippers
and handles increases, the number of states in the constraint may increase very
quickly. Using python bindings, it is possible however to define constraint
graphs with only the necessary states. We now present a test case that
illustrates this possibility.

In this example, an operator provides the sequence of actions (transitions)
the system needs to go through:
\begin{enumerate}
\item robot 1 grasps sphere 1,
\item robot 2 grasps cylinder 1,
\item robot 1 sticks sphere 1 on cylinder 1,
\item robot 1 releases sphere 1,
\item robot 1 grasps sphere 2,
\item robot 1 sticks sphere 2 on cylinder 1,
\item robot 1 releases sphere 2,
\item robot 2 put cylinder 1 on the ground.
\end{enumerate}
From this sequence of actions, the sequence of states visited is
computed and only those states (9 in total) are built in the
constraint graph. Then, a sequence of subgoals in the successive
states is computed, in such a way that each sub-goal is accessible by
the previous one (on the same leaf of the corresponding transition
foliation). The subgoals are then linked by running a constrained visibility
PRM algorithm (\cite{SimLauNis00}) on each leaf. The python code can be found
on \href{https://github.com/humanoid-path-planner/hpp_benchmark/blob/master/2020-07-23/construction-set/script.py}{github.com}.

Figure~\ref{fig:construction-set} displays the initial configuration and the
goal state. Table~\ref{tab:construction-set} shows the experimental results.

\subsubsection{Analysis}

The experimental results show that M-RRT is able to solve a variety of
manipulation problems including with a legged robots in quasi-static
equilibrium. No parameter tuning is required between the different problems. All
parameters are set to a default value for all test cases.

As for any random motion planning method, we observe a large standard
deviation within the 20 runs of each test case, both for the number of nodes
and for the time of computation.

We have also observed experimentally that the efficiency of M-RRT decreases
when
\begin{enumerate}
\item the number of states to visit to solve a problem increases,
\item the number of foliated states increases.
\end{enumerate}
For this reason, M-RRT is not able to solve the construction set
problem in a reasonable amount of time. It remains to our knowledge
the only algorithm in the literature able to solve a variety of
problems as large as those exposed in this section.
